A data-driven, pixel-level model to improve the precision of \Kepler\ photometry

### 2013-10-15 documents/plm.tex
todo items

[General formula here for a pixel predicted using a linear combination of other pixels.
  And the objective function, generally?]

@@

% need to choose consistent notation or terminology about the contiguous data chunks.

>>>>

\todo{Should we put general formula here for a pixel predicted using a linear combination of other pixels?
  And the objective function, generally?}

@@

\todo{In what follows, we need to choose consistent notation or terminology about the contiguous data chunks, and other \Kepler\ entities.}
